\textit{F1000Research} A studyforrest extension, an annotations of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-05 paper/main.tex
add preliminary figure "slicescolorbars" below tables in main.tex
add preliminary tables of significant clusters

\clearpage
\begin{table*}[t]
\caption{Overview of the speech annotation's content for the whole stimulus and it's individual segments. Words include \aPosNonspeechAll\space non-speech vocalizations.}
\label{tab:example}
\begin{tabular}{llllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
sentences  & \aSentencesAll & \aSentencesI & \aSentencesII & \aSentencesIII & \aSentencesIV & \aSentencesV & \aSentencesVI & \aSentencesVII & \aSentencesVIII \tabularnewline
words  & \aWordsAll & \aWordsI & \aWordsII & \aWordsIII & \aWordsIV & \aWordsV & \aWordsVI & \aWordsVII & \aWordsVIII \tabularnewline
phonemes  & \aPhonesAll & \aPhonesI & \aPhonesII & \aPhonesIII & \aPhonesIV & \aPhonesV & \aPhonesVI & \aPhonesVII & \aPhonesVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

    \caption{Narrator's descriptive nouns. All categories sorted alphapetically. Examples are given in English. Description (of rules) fehlt in dieser Tabelle (vgl. alte Tabelle auf der allerletzten Seite). Wird nämlich in einer Tabelle mit horizontaler Ausrichtung eng. Kategorie ```++''' enthält ausnahmesweise auch adverbiale Best. der Zeit'''.}

@@

setting\_new  & \aDescrSettingnewAll & \aDescrSettingnewI & \aDescrSettingnewII & \aDescrSettingnewIII & \aDescrSettingnewIV & \aDescrSettingnewV & \aDescrSettingnewVI & \aDescrSettingnewVII & \aDescrSettingnewVIII & on a ```bridge''', on an ```alley''', on ```campus''' \tabularnewline
setting\_rec  & \aDescrSettingrecAll & \aDescrSettingrecI & \aDescrSettingrecII & \aDescrSettingrecIII & \aDescrSettingrecIV & \aDescrSettingrecV & \aDescrSettingrecVI & \aDescrSettingrecVII & \aDescrSettingrecVIII & at the ```bus stop''' \tabularnewline
++  & \aDescrAll & \aDescrI & \aDescrII & \aDescrIII & \aDescrIV & \aDescrV & \aDescrVI & \aDescrVII & \aDescrVIII & in the ```evening''', it's ```daytime''', ```later''' \tabularnewline

@@

\caption{Overview of the 26 REGRESSORS used for the validation analysis. The top 20 categories of the detailed part-of speech tagging were used as such. Descriptions were taken from spaCy.explain(). All others tags were pooled to ```tag\_other'''. The other categories were build\dots}

@@

24 & no-sp  & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII & no speech (```soundscape''') \tabularnewline

@@

% Also weshalb wird das temporal filtering der regressoren wann wie gemacht??? -> nachschlagen
% “You should normally apply the same temporal filtering to the model as you have applied to the data, as the model is designed to look like the data before temporal filtering was applied. In this way, long-time-scale components in the model will be dealt with correctly. This is set with the Apply temporal filtering option.”
\begin{figure*}
  \centering
% \includegraphics[width=0.4\textwidth]{frog.jpg}
  \includegraphics[width=\linewidth]{figures/regressor-corr}
  \caption{Pearson correlation coefficients of the 26 regressors used in the analysis to validate the annotation. Regressors were convolved with FSL's “Double-Gamma HRF” as a model of the hemodynamic response function, temporally filtered with the same high-pass filter (cut-off 150s) as the BOLD time series, and cocatenated across runs before performing the correlation. Die unterschiedlichen Farben in den der Schriften kann man noch (wie?) sinnvoll ändern.}
  \label{fig:correlation}
\end{figure*}

\clearpage
\section*{Introduction}
% Links sind jetzt im laufenden Text; habs nach wie vor mit \href gemacht
% sieht bei längeren Links natürlich kacke aus

>>>>

\clearpage

\begin{table*}[t]
\caption{Overview of the speech annotation's content for the whole stimulus and it's individual segments. Words include \aPosNonspeechAll\space non-speech vocalizations.}
\label{tab:example}
\begin{tabular}{llllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
sentences  & \aSentencesAll & \aSentencesI & \aSentencesII & \aSentencesIII & \aSentencesIV & \aSentencesV & \aSentencesVI & \aSentencesVII & \aSentencesVIII \tabularnewline
words  & \aWordsAll & \aWordsI & \aWordsII & \aWordsIII & \aWordsIV & \aWordsV & \aWordsVI & \aWordsVII & \aWordsVIII \tabularnewline
phonemes  & \aPhonesAll & \aPhonesI & \aPhonesII & \aPhonesIII & \aPhonesIV & \aPhonesV & \aPhonesVI & \aPhonesVII & \aPhonesVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

    \caption{Narrator's descriptive nouns. All categories sorted alphapetically. Examples are given in English. Description (of rules) fehlt in dieser Tabelle (vgl. alte Tabelle auf der allerletzten Seite). Wird nämlich in einer Tabelle mit horizontaler Ausrichtung eng. Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der Zeit.}

@@

setting\_new  & \aDescrSettingnewAll & \aDescrSettingnewI & \aDescrSettingnewII & \aDescrSettingnewIII & \aDescrSettingnewIV & \aDescrSettingnewV & \aDescrSettingnewVI & \aDescrSettingnewVII & \aDescrSettingnewVIII & on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
setting\_rec  & \aDescrSettingrecAll & \aDescrSettingrecI & \aDescrSettingrecII & \aDescrSettingrecIII & \aDescrSettingrecIV & \aDescrSettingrecV & \aDescrSettingrecVI & \aDescrSettingrecVII & \aDescrSettingrecVIII & at the ``bus stop'' \tabularnewline
++  & \aDescrAll & \aDescrI & \aDescrII & \aDescrIII & \aDescrIV & \aDescrV & \aDescrVI & \aDescrVII & \aDescrVIII & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline

@@

\caption{Overview of the 26 REGRESSORS used for the validation analysis. The top 20 categories of the detailed part-of speech tagging were used as such. Descriptions were taken from spaCy.explain(). All others tags were pooled to ``tag\_other''. The other categories were build\dots}

@@

24 & no-sp  & \rNospAll & \rNospI & \rNospII & \rNospIII & \rNospIV & \rNospV & \rNospVI & \rNospVII & \rNospVIII & no speech (``soundscape'') \tabularnewline

@@

% Also weshalb wird das temporal filtering der regressoren wann wie gemacht??? -> nachschlagen
% “You should normally apply the same temporal filtering to the model as you have applied to the data, as the model is designed to look like the data before temporal filtering was applied. In this way, long-time-scale components in the model will be dealt with correctly. This is set with the Apply temporal filtering option.”
\begin{figure*}
  \centering
% \includegraphics[width=0.4\textwidth]{frog.jpg}
  \includegraphics[width=\linewidth]{figures/regressor-corr}
  \caption{Pearson correlation coefficients of the 26 regressors used in the analysis to validate the annotation. Regressors were convolved with FSL's “Double-Gamma HRF” as a model of the hemodynamic response function, temporally filtered with the same high-pass filter (cut-off 150s) as the BOLD time series, and cocatenated across runs before performing the correlation. NOTE: Bisher werden pdf figures. Die unterschiedlichen Farben in den der Schriften kann man noch (wie?) sinnvoll ändern.}
  \label{fig:correlation}
\end{figure*}

\begin{figure*}
  \centering
% \includegraphics[width=0.4\textwidth]{frog.jpg}
  \includegraphics[width=\linewidth]{figures/slicescolorbars}
  \caption{Mixed-effects group-level (N=14) GLM contrasts for the audio-description of the movie Forrest Gump. All cluster (Z>3.4, p<0.05; cluster corr.; MNI template space).}
  \label{fig:results}
\end{figure*}

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for COPE1: all 21 tag-related regressors > no speech.}
\begin{tabular}{rrrrrrrrrrp{3cm}}
\toprule
& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{5-7} \cmidrule{8-10}
Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
\midrule
4 & 14990 & 0 & 6.31 & -49 & -24.7 & 6.35 & -54.8 & -32.5 & 3.73 & AREAL \\
3 & 14469 & 0 & 6.48 & 55 & -14.9 & -6.9 & 54.1 & -23.1 & 0.374 & AREAL \\
2 & 1971 & 2.37E-16 & 5.26 & -51.1 & 25.6 & -10.5 & -53.6 & 17.8 & 10.2 & AREAL \\
1 & 217 & 0.00214 & 4.55 & -4.48 & -13.7 & 10.3 & -6.46 & -14.9 & 9.96 & AREAL \\
\bottomrule
\end{tabular}
\label{tab:cope1}
\end{table*}

\begin{table*}[t]
\caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for COPE3: proper nouns (``ne'') > coordinate conjunctions (``kon'').}
\begin{tabular}{rrrrrrrrrrp{3cm}}
\toprule
& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{5-7} \cmidrule{8-10}
Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
\midrule
9 & 7691 & 2.80E-45 & 6.23 & -61.2 & -22.3 & 11.6 & -55.9 & -20.7 & 4.03 & AREAL \\
8 & 5928 & 5.97E-38 & 5.5 & 57.5 & -26.2 & 15.9 & 58.2 & -15.8 & 3.55 & AREAL \\
7 & 479 & 1.13E-06 & 4.62 & -5.42 & -32.3 & 25.3 & -4.28 & -39.4 & 22.8 & AREAL \\
6 & 420 & 4.65E-06 & 4.85 & -4.76 & -71.4 & 40.1 & -3.74 & -68.5 & 36.2 & AREAL \\
5 & 407 & 6.38E-06 & 5.07 & 6.83 & -40.1 & 24.5 & 6.67 & -38.7 & 23.1 & AREAL \\
4 & 294 & 0.000115 & 4.57 & 17 & -69.1 & 34.6 & 17.7 & -67.1 & 34.9 & AREAL \\
3 & 121 & 0.0237 & 3.95 & 8.12 & -98.2 & 0.359 & 8.75 & -97.7 & -3.15 & AREAL \\
2 & 117 & 0.0274 & 4.38 & 36.9 & -24.8 & 4.55 & 37.4 & -23 & 3.09 & AREAL \\
1 & 115 & 0.0295 & 4.08 & -44.6 & -71.7 & 21.7 & -43.6 & -70.8 & 23.4 & AREAL \\
\bottomrule
\end{tabular}
\label{tab:cope3}
\end{table*}

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05; corrected) for COPE5: nouns (``nn'') > coordinate conjunctions (``kon'').}
\begin{tabular}{rrrrrrrrrrp{3cm}}
\toprule
& & & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{5-7} \cmidrule{8-10}
Cl.\-Index & Voxels & $p_{corr.}$ & Z\-max & X & Y & Z  & X & Y & Z & structure \\
\midrule
4 & 3166 & 2.79E-25 & 5.75 & -61.3 & -10.6 & -2.93 & -57.7 & -14.3 & 1.47 & AREAL \\
3 & 1753 & 7.18E-17 & 4.99 & 63.3 & -15.1 & 8.41 & 58 & -13 & 4.02 & AREAL \\
2 & 166 & 0.00446 & 4.5 & 6.83 & -40.1 & 24.5 & 7.01 & -39.7 & 24.2 & AREAL \\
1 & 149 & 0.00793 & 4.13 & 18.2 & -67.8 & 36 & 19.8 & -66.4 & 34.6 & AREAL \\
\bottomrule
\end{tabular}
\label{tab:cope5}
\end{table*}

\clearpage

\section*{Introduction}
% Links sind jetzt im laufenden Text; habs nach wie vor mit \href gemacht
% sieht bei längeren Links natürlich kacke aus
